\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdfborder={0 0 0}
}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lipsum}
\usepackage[left=1.5cm,top=1.2cm,right=1.5cm,bottom=1.2cm]{geometry}

\begin{document}

% Header
\begin{minipage}[t]{0.33\textwidth}
    \raggedright
    District 8, Ho Chi Minh City\\
    \href{tel:+84388227064}{(+84) 388227064}
\end{minipage}%
\begin{minipage}[t]{0.34\textwidth}
    \centering
    \textbf{\Large Tran Thanh Hiep}\\
    \textbf{\large Junior Fullstack Developer}
\end{minipage}%
\begin{minipage}[t]{0.33\textwidth}
    \raggedleft
    \href{mailto:hiepthanhtran.2003@gmail.com}{hiepthanhtran.2003@gmail.com}\\
    \href{https://www.linkedin.com/in/hjtrannn}{Linkedin - in/hjtrannn}\\
    \href{https://github.com/marshallvoid}{Github - marshallvoid}
\end{minipage}

\vspace{0.15cm}

% Objective
\begin{center}
    \textbf{Objective}
\end{center}
\vspace{-0.1cm}

Seeking a \textbf{Software Engineer} role to leverage expertise in \textbf{full-stack development, microservices architecture, and cloud technologies} to build \textbf{scalable, high-performance systems}. Passionate about delivering innovative solutions and driving measurable business impact through modern engineering practices.

\vspace{0.1cm}

% Education
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-0.1cm}

\textbf{Ho Chi Minh City Open University} \hfill \textbf{HCMOU}

Bachelor in Computer Science. GPA: 3.39 / 4.0 \hfill 10/2024 -- 09/2025

Relevant Coursework: Data Structures \& Algorithms, Object-Oriented Programming, Databases, Design Patterns.

\vspace{0.1cm}

% Technical Skills
\begin{center}
    \textbf{Technical Skills}
\end{center}
\vspace{-0.1cm}

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=1.5em]
    \item \textbf{Languages}: Python, JavaScript, TypeScript, Java, SQL
    \item \textbf{Frameworks}: React.js, Next.js, FastAPI, Django, Flask, Spring Boot, Vue.js
    \item \textbf{Databases}: PostgreSQL, MySQL, Redis, Neo4j, MongoDB
    \item \textbf{Tools \& Cloud}: Docker, Git, AWS S3, Firebase, RabbitMQ, NATS, Celery
\end{itemize}

\vspace{0.1cm}

% Experience
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-0.1cm}

\textbf{True Digital Vietnam} (\href{https://www.smartkoc.com/}{smartkoc.com}) \hfill District 2, Ho Chi Minh City

\hspace{1em}\textbf{Fullstack Developer} (Fulltime) \hfill 10/2024 -- 12/2025

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=1.5em]
    \item Built \textbf{AI-powered influencer matching system} using LangChain and LangGraph to analyze campaign briefs and generate creator recommendations with LLM providers (OpenAI, Anthropic, Google Gemini), and developed video analysis system using DSPy for content quality scoring with MLflow experiment tracking.
    \item Created \textbf{FastAPI backend} with NATS Faststream for async messaging and \textbf{Django REST API} with Celery for background task processing, implementing project management features with PostgreSQL, Redis, and MinIO/S3 storage.
    \item Designed \textbf{Next.js frontend} with React and MobX state management for creator platform, integrating real-time analytics and content management interfaces.
    \item Implemented \textbf{TikTok Affiliate web scraper} using Playwright with stealth techniques, anti-detection measures, and CAPTCHA solving to extract creator marketplace data, handling authentication flows, request interception, and automated data collection with human behavior simulation.
    \item \textbf{Tech Stack}: FastAPI, Django, PostgreSQL, Redis, NATS, Celery, Next.js, React, TypeScript, Docker, AWS S3.
\end{itemize}

\vspace{0.1cm}

% Projects
\begin{center}
    \textbf{Projects}
\end{center}
\vspace{-0.1cm}

\textbf{HarmonyChain - Supply Chain Management System} \hfill \href{https://github.com/marshallvoid/harmony-chain}{marshallvoid/harmony-chain}

\hspace{1em}\textbf{Fullstack Developer}

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=1.5em]
    \item Architected \textbf{microservices system} with 11 Spring Boot services (Identity, Product, Order, Cart, Inventory, Shipment, Rating, Notification, Profile, File, API Gateway) with event-driven architecture and centralized API Gateway.
    \item Built \textbf{CI/CD pipelines} using GitHub Actions for automated testing, building, and deployment with Docker containerization for each microservice.
    \item Developed \textbf{Next.js frontend} with TypeScript and TailwindCSS, integrating AWS S3, Brevo email automation, and Stripe payment processing.
    \item \textbf{Tech Stack}: Spring Boot, Next.js, TypeScript, TailwindCSS, Docker, GitHub Actions, AWS S3, Stripe, Brevo, RESTful API.
\end{itemize}

\vspace{0.1cm}

\textbf{Trainify - Training Point Management System} \hfill \href{https://github.com/marshallvoid/trainify-app}{marshallvoid/trainify-app} | \href{https://github.com/marshallvoid/trainify-app-backend}{trainify-app-backend}

\hspace{1em}\textbf{Fullstack Developer}

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=1.5em]
    \item Built \textbf{student conduct point tracking system} for educational institutions with role-based access for student affairs specialists, assistants, and students.
    \item Developed \textbf{Django REST API backend} with OAuth2 authentication using django-oauth-toolkit, implementing secure user access and role-based authorization for activity registration and point tracking with comprehensive API documentation via Swagger.
    \item Created \textbf{React Native mobile app} with Firebase integration for real-time chat, push notifications, and cloud storage, providing comprehensive reporting and account management features.
    \item \textbf{Tech Stack}: Django, React Native, OAuth2, MySQL, Firebase, Cloudinary, RESTful API, Swagger.
\end{itemize}

\end{document}
